Thesis Title

### 2022-04-22 main.tex

%-----------------------------------------------------------------
% Thesis Outline
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Thesis Outline}
\chapter*{Thesis Outline}
\input{chapters/thesis_outline}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

%-----------------------------------------------------------------
% Abbreviations
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Abbreviation}
\chapter*{Abbreviation}
\input{chapters/acconyms}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

@@

%-----------------------------------------------------------------
% Introduction
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{General Introduction\label{ch:introduction}}
\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/introduction}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Paper 1
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{Critical steps in clinical shotgun metagenomics for the concomitant detection and typing of microbial pathogens\label{ch:paper1}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/chapter_2}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Paper 2
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{Detection of a novel \textit{mcr-5.4} gene variant in hospital tap water by shotgun metagenomic sequencing\label{ch:paper2}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/chapter_3}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Paper 3
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{DEN-IM: Dengue virus genotyping from shotgun and targeted metagenomics\label{ch:paper3}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/chapter_4}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

>>>>

%-----------------------------------------------------------------
% Thesis Outline
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Thesis Outline}
\chapter*{Thesis Outline}
%\input{chapters/thesis_outline}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

%-----------------------------------------------------------------
% Abbreviations
%------------------------------------------------------------------
\newpage
\thispagestyle{plain}
\addcontentsline{toc}{chapter}{Abbreviation}
\chapter*{Abbreviation}
I \input{chapters/acconyms}
\clearpage \thispagestyle{empty}\mbox{}\clearpage

@@

%-----------------------------------------------------------------
% Introduction
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{General Introduction\label{ch:introduction}}
\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
%\include{chapters/introduction}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Paper 1 - Natacha
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{Critical steps in clinical shotgun metagenomics for the concomitant detection and typing of microbial pathogens\label{ch:paper1}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
%\include{chapters/chapter_2}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Paper 2 - Peppe
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{Detection of a novel \textit{mcr-5.4} gene variant in hospital tap water by shotgun metagenomic sequencing\label{ch:paper2}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
%\include{chapters/chapter_3}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Paper 3 - DEN-IM
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{DEN-IM: Dengue virus genotyping from shotgun and targeted metagenomics\label{ch:paper3}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
%\include{chapters/chapter_4}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Paper 4 - LMAS
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{LMAS: Last Metagenomic Assembler Standing\label{ch:paper4}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
%\include{chapters/chapter_5}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Paper 5 - hAMRonization
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{hAMRonization: Enhancing antimicrobial resistance prediction using PHA4GE standards and specification\label{ch:paper5}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
%\include{chapters/chapter_6}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}

%-----------------------------------------------------------------
% Paper 6 - SARS-CoV-2
%------------------------------------------------------------------
\newpage
\thispagestyle{empty}
\chapter{Future-proofing and maximising the utility of metadata: The PHA4GE SARS-CoV-2 contextual data specification package\label{ch:paper6}}

\thispagestyle{empty}
\clearpage \thispagestyle{empty}\mbox{}\clearpage
\newpage
\begin{refsection}
\include{chapters/chapter_7}
\newpage
\section{References}
\printbibliography[heading=none]
\end{refsection}
